%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
\usepackage{booktabs} % For formal tables
\usepackage{amsmath}
\usepackage[noend]{algpseudocode}
\usepackage[flushleft]{threeparttable}
\usepackage{subfigure}
\usepackage{comment}
\usepackage{color}
\usepackage{soul}
\usepackage{hyperref}
\usepackage{url}
\usepackage{multirow}
\usepackage[lined,linesnumbered,ruled]{algorithm2e}
\usepackage[flushleft]{threeparttable}
\usepackage{mfirstuc}
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
\makeatletter
\def\th@plain{%
  \thm@notefont{}% same as heading font
  \itshape % body font
}
\def\th@definition{%
  \thm@notefont{}% same as heading font
	\itshape
}
\makeatother

\newtheorem{Def}{Definition}%[section]
\newcommand{\Defautorefname}{Definition}
\newtheorem{Thm}{Theorem}%[section]
\newcommand{\Thmautorefname}{Theorem}
\newcommand{\ie}{i.e., }
\newcommand{\eg}{e.g., }
\newcommand{\usernote}[1]{\textbf{\color{blue}[***** #1 *****]\\}}

% Problem specific macros
\newcommand{\probdef}{k-truss community search}
\newcommand{\Probdef}{K-truss community search}
\newcommand{\ProbDef}{\expandafter\capitalisewords\expandafter{\probdef}}
\newcommand{\inducedgraph}{induced MST graph}
\newcommand{\Inducedgraph}{Induced MST graph}
\newcommand{\InducedGraph}{\expandafter\capitalisewords\expandafter{\inducedgraph}}
\newcommand{\treeindex}{tree-structured community graph}
\newcommand{\Treeindex}{Tree-structured community graph}
\newcommand{\TreeIndex}{\expandafter\capitalisewords\expandafter{\treeindex}}

%
% Insert the name of "your journal" with
\journalname{Data Mining and Knowledge Discovery}
%
\begin{document}

\title{Fast Truss Community Query in Large-scale Dynamic Graphs%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{Zheng Lu         \and
				Yunhe Feng			 \and
        Qing Cao %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Zheng Lu \at
							Electrical Engineering \& Computer Science, University of Tennessee \\
              % Tel.: +123-45-678910\\
              % Fax: +123-45-678910\\
              \email{zlu12@vols.utk.edu}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
					 Zheng Lu \at
							Electrical Engineering \& Computer Science, University of Tennessee \\
							\email{yfeng14@vols.utk.edu} 
           Qing Cao \at
							Electrical Engineering \& Computer Science, University of Tennessee \\
							\email{cao@utk.edu} 
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor


\maketitle

\begin{abstract}
Recently, there has been significant interest in the study of the community search problem in social and information networks: given one or more query nodes, find densely connected communities containing the query nodes. However, most existing algorithms require linear computational time to the size of the found community for each specific K value. Therefore, state-of-the-art algorithms have limited scalability in large scale graphs, where communities grow to millions of edges.

In this paper, given an undirected graph G and a set of query
nodes $Q$, we study community query using the k-truss based community model. We formulate our problem of finding a connected truss community, as finding a connected k-truss subgraph with all possible k that contains Q. The state-of-art approximation algorithm can achieve this goal with a time complexity of $O(n'm')$ where $n'$ and $m'$ are the size of the result truss community. For queries that only identity and exact size of communities are required, We construct an index structure that can retrieve there information of all connected k-truss communities that contain $Q$ with all possible K values. The algorithm can run in $\sum_{u \in Q} d(u)$, where $d(u)$ is the degree of vertex $u$. We prove that this is the optimal time complexity for truss community query. Extensive experiments on real-world networks show the effectiveness and efficiency of our algorithms. 
\keywords{K-truss \and dynamic graph \and query process}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\input{introduction}
\input{preliminary}
\input{index}
\input{query}
\input{evaluation}
\input{relatedwork}
\input{conclusion}

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% BibTeX users please use one of
\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{reference}   % name your BibTeX data base

\end{document}
% end of file template.tex

