\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[flushleft]{threeparttable}
\usepackage{subfigure}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


%% DOI
%\acmDOI{10.475/123_4}
%
%% ISBN
%\acmISBN{123-4567-24-567/08/06}
%
%%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
  %Paso, Texas USA} 
%\acmYear{1997}
%\copyrightyear{2016}
%
%\acmPrice{15.00}
%

%\newtheorem{theorem}{Theorem}

\begin{document}
\title{Fast Truss Community Query in Large-scale Dynamic Graphs}
%\titlenote{Produces the permission block, and
  %copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
  %\texttt{acmart.pdf} document}


\author{Zheng Lu}
\affiliation{%
  \institution{University of Tennessee}
  \department{Electrical Engineering and Computer Science}
}
\email{zlu12@vols.utk.edu}

\author{Qing Cao}
\affiliation{%
  \institution{University of Tennessee}
  \department{Electrical Engineering and Computer Science}
}
\email{cao@utk.edu}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{Z. Lu et al.}


\begin{abstract}
Recently, there has been significant interest in the study of the community search problem in social and information networks: given one or more query nodes, find densely connected communities containing the query nodes. However, most existing algorithms require linear computational time to the size of the found community for each specific K value. Therefore, state-of-the-art algorithms have limited scalability in large scale graphs, where communities grow to millions of edges.

In this paper, given an undirected graph G and a set of query
nodes $Q$, we study community query using the k-truss based community model. We formulate our problem of finding a connected truss community, as finding a connected k-truss subgraph with all possible k that contains Q. The state-of-art approximation algorithm can achieve this goal with a time complexity of $O(n'm')$ where $n'$ and $m'$ are the size of the result truss community. For queries that only identity and exact size of communities are required, We construct an index structure that can retrieve there information of all connected k-truss communities that contain $Q$ with all possible K values. The algorithm can run in $\sum_{u \in Q} d(u)$, where $d(u)$ is the degree of vertex $u$. We prove that this is the optimal time complexity for truss community query. Extensive experiments on real-world networks show the effectiveness and efficiency of our algorithms. 
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
%\begin{CCSXML}
%<ccs2012>
 %<concept>
  %<concept_id>10010520.10010553.10010562</concept_id>
  %<concept_desc>Computer systems organization~Embedded systems</concept_desc>
  %<concept_significance>500</concept_significance>
 %</concept>
 %<concept>
  %<concept_id>10010520.10010575.10010755</concept_id>
  %<concept_desc>Computer systems organization~Redundancy</concept_desc>
  %<concept_significance>300</concept_significance>
 %</concept>
 %<concept>
  %<concept_id>10010520.10010553.10010554</concept_id>
  %<concept_desc>Computer systems organization~Robotics</concept_desc>
  %<concept_significance>100</concept_significance>
 %</concept>
 %<concept>
  %<concept_id>10003033.10003083.10003095</concept_id>
  %<concept_desc>Networks~Network reliability</concept_desc>
  %<concept_significance>100</concept_significance>
 %</concept>
%</ccs2012>  
%\end{CCSXML}
%
%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}

% We no longer use \terms command
%\terms{Theory}
%
%\keywords{ACM proceedings, \LaTeX, text tagging}


\maketitle

\input{introduction}
\input{relatedwork}
\input{preliminary}
\input{induced_graph}
\input{index}
\input{evaluation}
\input{conclusion}

\bibliographystyle{ACM-Reference-Format}
\bibliography{reference} 

\end{document}
