\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
%%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs} % For formal tables
%%\usepackage{amsmath}
\usepackage[noend]{algpseudocode}
\usepackage[flushleft]{threeparttable}
\usepackage{subfigure}
\usepackage{comment}
\usepackage{color}
\usepackage{soul}
\usepackage{hyperref}
\usepackage{url}
\usepackage{multirow}
\usepackage[lined,linesnumbered,ruled]{algorithm2e}
\usepackage[flushleft]{threeparttable}
\usepackage{mfirstuc}
\usepackage{tabularx}
%\usepackage{natbib}

\newtheorem{Def}{Definition}%[section]
\newcommand{\Defautorefname}{Definition}
\newtheorem{Thm}{Theorem}%[section]
\newcommand{\Thmautorefname}{Theorem}
\newtheorem{Obs}{Observation}%[section]
\newcommand{\Obsautorefname}{Observation}
\newcommand{\ie}{i.e., }
\newcommand{\eg}{e.g., }
%\newcommand{\usernote}[1]{\textbf{\color{blue}[#1]}}

\newcolumntype{Y}{>{\centering\arraybackslash}X}

% Paper specific macros
\newcommand{\probdef}{local k-truss community query}
\newcommand{\Probdef}{Local k-truss community query}
\newcommand{\ProbDef}{\expandafter\capitalisewords\expandafter{\probdef}}
\newcommand{\toplevelprob}{community-level}
\newcommand{\Toplevelprob}{Community-level}
\newcommand{\TopLevelProb}{\expandafter\capitalisewords\expandafter{\toplevelprob}}
\newcommand{\bottomlevelprob}{edge-level}
\newcommand{\Bottomlevelprob}{Edge-level}
\newcommand{\BottomLevelProb}{\expandafter\capitalisewords\expandafter{\bottomlevelprob}}

\newcommand{\twolevelindex}{2-level index}
\newcommand{\Twolevelindex}{2-level index}
\newcommand{\TwoLevelIndex}{\expandafter\capitalisewords\expandafter{\twolevelindex}}

\newcommand{\inducedgraph}{triangle derived graph}
\newcommand{\Inducedgraph}{triangle derived graph}
\newcommand{\InducedGraph}{\expandafter\capitalisewords\expandafter{\inducedgraph}}
\newcommand{\treeindex}{community graph}
\newcommand{\Treeindex}{community graph}
\newcommand{\TreeIndex}{\expandafter\capitalisewords\expandafter{\treeindex}}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{2-level Index for Truss Community Query in Large-Scale Graphs}

\author{\IEEEauthorblockN{Zheng Lu, Yunhe Feng, Qing Cao}
\IEEEauthorblockA{\textit{Dept. of Electrical Engineering \& Computer Science}, \textit{University of Tennessee}, Knoxville, USA \\
\{zlu12, yfeng14, cao\}@utk.edu}
%\and
%\IEEEauthorblockN{Yunhe Feng}
%\IEEEauthorblockA{\textit{Dept. of Electrical Engineering \& Computer Science} \\
%\textit{University of Tennessee}\\
%Knoxville, USA \\
%yfeng14@vols.utk.edu}
%\and
%\IEEEauthorblockN{Qing Cao}
%\IEEEauthorblockA{\textit{Dept. of Electrical Engineering \& Computer Science} \\
%\textit{University of Tennessee}\\
%Knoxville, USA \\
%cao@utk.edu}
}

\maketitle

\begin{abstract}
Recently, there are significant interests in the study of the community search problem in large-scale graphs. K-truss as a community model has drawn increasing attention in the literature. In this work, we extend our scope from the community search problem to more generalized local community query problems based on triangle connected k-truss community model. We classify local community query into two categories, the \toplevelprob{} query and the \bottomlevelprob{} query based on the information required to process a community query. We design a 2-level index structure that stores k-truss community relations in the top level index and preserves triangle connectivity between edges in the bottom level index. 
The proposed index structure not only can process both \toplevelprob{} queries and \bottomlevelprob{} queries in optimal time but also can handle both single-vertex queries and multiple-vertex queries. We conduct extensive experiments using real-world large-scale graphs and compare with state-of-the-art methods for k-truss community search. Results show our method can process \toplevelprob{} queries in the range of hundreds of microseconds to less than a second and \bottomlevelprob{} queries from a few seconds to hundreds of seconds for highest degree vertices within large communities.
\end{abstract}

\begin{IEEEkeywords}
Query-dependent community detection, K-truss, Large-scale graphs
\end{IEEEkeywords}

\input{introduction}
\input{preliminary}
\input{index}
\input{query}
\input{evaluation}
\input{relatedwork}
\input{conclusion}

\bibliographystyle{abbrv}
\bibliography{reference}
%\input{appendix}

\end{document}
