\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
%%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs} % For formal tables
%%\usepackage{amsmath}
%\usepackage[noend]{algpseudocode}
\usepackage[flushleft]{threeparttable}
\usepackage{subfigure}
\usepackage{comment}
\usepackage{color}
\usepackage{soul}
\usepackage{hyperref}
\usepackage{url}
\usepackage{multirow}
\usepackage[lined,linesnumbered,ruled,noend]{algorithm2e}
\usepackage[flushleft]{threeparttable}
\usepackage{mfirstuc}
\usepackage{tabularx}
%\usepackage{natbib}

\newtheorem{Def}{Definition}%[section]
\newcommand{\Defautorefname}{Definition}
\newtheorem{Thm}{Theorem}%[section]
\newcommand{\Thmautorefname}{Theorem}
\newtheorem{Obs}{Observation}%[section]
\newcommand{\Obsautorefname}{Observation}
\newcommand{\ie}{i.e., }
\newcommand{\eg}{e.g., }
%\newcommand{\usernote}[1]{{\color{blue}#1}}

\newcolumntype{Y}{>{\centering\arraybackslash}X}

% Paper specific macros
\newcommand{\probdef}{local k-truss community query}
\newcommand{\Probdef}{Local k-truss community query}
\newcommand{\ProbDef}{\expandafter\capitalisewords\expandafter{\probdef}}
\newcommand{\toplevelprob}{community-level}
\newcommand{\Toplevelprob}{Community-level}
\newcommand{\TopLevelProb}{\expandafter\capitalisewords\expandafter{\toplevelprob}}
\newcommand{\bottomlevelprob}{edge-level}
\newcommand{\Bottomlevelprob}{Edge-level}
\newcommand{\BottomLevelProb}{\expandafter\capitalisewords\expandafter{\bottomlevelprob}}

\newcommand{\twolevelindex}{two-level index}
\newcommand{\Twolevelindex}{Two-level index}
\newcommand{\TwoLevelIndex}{\expandafter\capitalisewords\expandafter{\twolevelindex}}

\newcommand{\inducedgraph}{triangle-derived graph}
\newcommand{\Inducedgraph}{Triangle-derived graph}
\newcommand{\InducedGraph}{\expandafter\capitalisewords\expandafter{\inducedgraph}}
\newcommand{\treeindex}{community graph}
\newcommand{\Treeindex}{Community graph}
\newcommand{\TreeIndex}{\expandafter\capitalisewords\expandafter{\treeindex}}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{\TwoLevelIndex{} for Truss Community Query in Large-Scale Graphs}

\author{\IEEEauthorblockN{Zheng Lu, Yunhe Feng, Qing Cao}
\IEEEauthorblockA{\textit{Dept. of Electrical Engineering \& Computer Science}, \textit{University of Tennessee}, Knoxville, USA \\
\{zlu12, yfeng14, cao\}@utk.edu}
%\and
%\IEEEauthorblockN{Yunhe Feng}
%\IEEEauthorblockA{\textit{Dept. of Electrical Engineering \& Computer Science} \\
%\textit{University of Tennessee}\\
%Knoxville, USA \\
%yfeng14@vols.utk.edu}
%\and
%\IEEEauthorblockN{Qing Cao}
%\IEEEauthorblockA{\textit{Dept. of Electrical Engineering \& Computer Science} \\
%\textit{University of Tennessee}\\
%Knoxville, USA \\
%cao@utk.edu}
}

\maketitle

\begin{abstract}
Recently, there has been a significant interest in the study of the community search problem in large-scale graphs. K-truss as a community model has drawn increasing attention in the literature. In this work, we extend our scope from the community search problems to a more generalized local community query problem based on a triangle-connected k-truss community model. We classify local community query into two categories, \toplevelprob{} and \bottomlevelprob{} query, based on the information required to process a given query. 
We design a two-level index structure that supports both types of queries with multiple query vertices and arbitrary cohesiveness criteria. 
We conduct extensive experiments using real-world large-scale graphs and compare with the state-of-the-art methods of k-truss community search. The results show that our method outperforms the state-of-the-art works in various types of local k-truss community queries. 
\end{abstract}

\begin{IEEEkeywords}
Query-dependent community detection, K-truss, Large-scale graphs
\end{IEEEkeywords}

\input{introduction}
\input{preliminary}
\input{index}
\input{query}
\input{evaluation}
\input{relatedwork}
\input{conclusion}

\bibliographystyle{abbrv}
\bibliography{reference}
%\input{appendix}

\end{document}
